### 2023-03-21 paper/localpsf.tex
wrote custom gmres function that can terminate when negative direction is encountered
added example description

>>>>

Here we consider a time-dependent advection-diffusion equation for
which we seek to infer an unknown initial contaminant field from
pointwise measurements of its concentration. The problem description
below closely follows the one in~\cite{PetraStadler11}. This PDE
models diffusive transport in a domain $\D \subset \R^d$, which is
depicted in Figure~\ref{fig:adv_inversion1}.  The domain
boundaries $\partial \D$ include the outer boundaries as well as the
internal boundaries of the rectangles, which represent buildings.  The
parameter-to-observable map $\iFF$ in this case maps an initial
condition $\ipar \in L^2(\D)$ to observations of the concentration
field $u(\vec{x}, t)$ through solution of the advection-diffusion
equation given by
\begin{equation}\label{eq:ad}
  \begin{aligned}
    u_t - \kappa\Delta u + \vec{v}\cdot\nabla u &= 0 & \quad&\text{in
    }\D\times (0,T), \\
    u(\cdot, 0) &= \ipar  &&\text{in } \D , \\
    \kappa\nabla u\cdot \vec{n} &= 0 &&\text{on } \partial\D \times (0,T).
  \end{aligned}
\end{equation}
Here, $\kappa > 0$ is a diffusivity coefficient, and $T > 0$ is the
final time of observations.  The velocity field $\vec{v}$, shown in
Figure~\ref{fig:adv_inversion1}, is computed by solving the
steady-state Navier-Stokes equations for a two dimensional flow with
Reynolds number 50 and boundary conditions as in
Figure~\ref{fig:adv_inversion} (left); see \cite{PetraStadler11} for
details.  The time evolution of the state variable $u$ from a given
initial condition $\ipar$ is illustrated in
Figure~\ref{fig:adv_inversion1}.
